High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-02 notebooks/gmsc.qmd
experiments

bmk = benchmark(
    counterfactual_data; 
    models=model_dict, 
    generators=generator_dict, 
    measure=measures,
    suppress_training=true, dataname="Californian Housing",
    n_individuals=5,
    factual=0, target=1,
    initialization=:identity,
)
CSV.write(joinpath(output_path, "gmsc_benchmark.csv"), bmk())
```

```{julia}
@chain bmk() begin
    @group_by(dataname, generator, model, variable)
    @summarize(mean=mean(value),sd=std(value))
    @ungroup
    @filter(variable == "distance_from_energy")
end
```

```{julia}
df = @chain bmk() begin
    @filter(variable in [
        "distance_from_energy",
        "distance_from_targets",
        "distance",])
    @mutate(variable = ifelse.(variable .== "distance_from_energy", "Non-Conformity", variable))
    @mutate(variable = ifelse.(variable .== "distance_from_targets", "Implausibility", variable))
    @mutate(variable = ifelse.(variable .== "distance", "Cost", variable))
end
plt = AlgebraOfGraphics.data(df) * visual(BoxPlot) * 
    mapping(:generator, :value, row=:variable, col=:model, color=:generator)
plt = draw(
    plt, axis=(xlabel="", xticksvisible=false, xticklabelsvisible=false, width=150, height=120), 
    facet=(; linkyaxes=:minimal)
)   
display(plt)
save(joinpath(output_images_path, "gmsc_benchmark.png"), plt, px_per_unit=5)
```

>>>>

bmk = benchmark(
    counterfactual_data; 
    models=model_dict, 
    generators=generator_dict, 
    measure=measures,
    suppress_training=true, dataname="Californian Housing",
    n_individuals=5,
    factual=0, target=1,
    initialization=:identity,
)
CSV.write(joinpath(output_path, "gmsc_benchmark.csv"), bmk.evaluation)
```

```{julia}
@chain bmk.evaluation begin
    @group_by(dataname, generator, model, variable)
    @summarize(mean=mean(value),sd=std(value))
    @ungroup
    @filter(variable == "distance_from_energy")
end
```

```{julia}
df = @chain bmk.evaluation begin
    @filter(variable in [
        "distance_from_energy",
        "distance_from_targets",
        # "distance",
    ])
    @mutate(variable = ifelse.(variable .== "distance_from_energy", "Non-Conformity", variable))
    @mutate(variable = ifelse.(variable .== "distance_from_targets", "Implausibility", variable))
    # @mutate(variable = ifelse.(variable .== "distance", "Cost", variable))
end
plt = AlgebraOfGraphics.data(df) * visual(BoxPlot) * 
    mapping(:generator, :value, row=:variable, col=:model, color=:generator)
plt = draw(
    plt, axis=(xlabel="", xticksvisible=false, xticklabelsvisible=false, width=150, height=120), 
    facet=(; linkyaxes=:minimal)
)   
display(plt)
save(joinpath(output_images_path, "gmsc_benchmark.png"), plt, px_per_unit=5)
```
